Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-18 manuscript/Chapter3-manuscript.Rmd
almost done par.1

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016]. Indeed, predator populations are often comprised of an assemblage of individuals that specialize in different foraging strategies or resources [@ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017]. Sexual and age related differences are common proximate factors underlying such among-individual variation, while environmental heterogeneity is known as a prevailing external factor [].

*les drivers connus (age, sex, etc.), mais quand on contrôle on voit que la spécxialisation est toujours là!!* *(finir en mettant l'accent sur le fait que les interactions modulent aussi, mais qu'on sait très peu comment ça interagit avec les facteurs proximaux)*

*Ideas* : 
- * usually measured at the population level*
- *effets de l'âge, blablabla*
- * we now have metrics that enable the quantification of individual specialization*

>>>>

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016]. Indeed, predator populations are often composed of an assemblage of individuals that specialize in different foraging strategies or resources [@estesIndividualVariationPrey2003, tinkerFoodLimitationLeads2008, kernaleguenDeterminantsIndividualForaging2015, @phillipsCausesConsequencesIndividual2017]. It is now well established that such individual specialization cannot be attributed exclusively to sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003, bolnickEcologyIndividualsIncidence2003, Woo.etal2008, bolnickWhyIntraspecificTrait2011]. Indeed, a growing body of evidence suggests that ecological interactions may act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011, @toscanoPersonalityForagingBehavior2016]. For instance, competition, cooperation, and predation, are all expected to shape the foraging preferences of interacting individuals []. Yet, we have very limited knowledge on how intrinsic factors and ecological interactions reciprocally affect foraging specialization, and the underlying consequences of such among-individual differences for natural populations. *phillips 2017*

*on connait peu sur l'interaction entre facteurs internes et externes, et encore moins les consequences de ces interactions (fitness, etc)*

sexual, morphological, or age-related differences, while environmental heterogeneity is a prevailing external factor [@Weimerskirch2007, @ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017, @Patrick.etal2021].

*les drivers connus (age, sex, etc.), mais quand on contrôle on voit que la spécialisation est toujours là!! (bolnick, araujo, woo)* *(finir en mettant l'accent sur le fait que les interactions modulent aussi, mais qu'on sait très peu comment ça interagit avec les facteurs proximaux)*

*Ideas* : 
- * we now have metrics that enable the quantification of individual specialization (cleasby)*
